---
title: "Community maps"
output: html_document
---

```{r libraries}
library(tidyverse)
library(dplyr)
library(plotly)
library(ggplot2)
library(sf)
library(httr)
```

## Load Plotly username and api key

```{r}
Sys.setenv("plotly_username"="xxxx")
Sys.setenv("plotly_api_key"="xxxx")
```

## Load csv file
```{r}
id4228 <-read_csv('../data/id4228_doc_count.csv') 
```

## Define custom function to cleanup column names

```{r}
colname_cleanup <- function(x) {
  colnames(x) <- x %>%
    colnames() %>%
    str_to_lower() %>% #make colnames lowercase
    str_replace_all(" ", "_") %>% #replace spaces with underscores
    str_replace_all("\\/", "_") #replace slashes with underscores
  ;x 
}
```

## Load zipcode shapefile

```{r}
#Fetch the .shp file from the full shapefile folder
sample_shapefile <- st_read('../data/zipcodes/geo_export_7afb9613-090f-4a4f-9066-1c8e7275dd9f.shp') %>%
  sf::st_transform('+proj=longlat +datum=WGS84')%>%
  colname_cleanup()

```
## Join the dataframe to the shapefile, dropping any unecessary columns
Be sure to do a full join to preserve the multipolygon data

```{r}
hca_df <- full_join(sample_shapefile,
                    sample_data%>%
                      mutate(zip=as.character(zip))
                    ) #%>% 
          #replace(is.na(.), 0) #replace all NAs in df with zeros for choropleth mapping
```

## Community HCA

```{r HCA and HTI from_npi}
hca_df %>%
  ggplot(aes(fill=patient_count)) +
  geom_sf(color=NA) + 
  scale_fill_viridis_c(option = "plasma", na.value = "grey60")+
  coord_sf(datum = NA) +
  labs(fill= 'Number of referrals',
      title = 'HCA') +
  theme_minimal()

#fig <- ggplotly(hca) not sure why it's not working
#fig

```

### Community Vanderbilt

```{r}
id4238_doc_data <-read_csv('../data/id4238_doc_count.csv') 
```

```{r}
id4238_doc_df <- full_join(sample_shapefile,
                    id4238_doc_data%>%
                      mutate(zip=as.character(zip))
                    ) %>% 
          replace(is.na(.), 0) #replace all NAs in df with zeros for choropleth mapping
```

```{r Vandy}
id4238_doc_df %>%
  ggplot(aes(fill=patient_count)) +
  geom_sf(color= "grey50") + #set 
  #coord_sf(crs=)
  scale_fill_gradientn(colours = c("white", "cyan", "magenta"), values = c(0,0.001,1)) +
  #scale_fill_viridis_c(option = "plasma", na.value = "grey60")+
  coord_sf(datum = NA) +
  labs(fill= 'Number of referrals',
      title = '  Vanderbilt University Medical Center')

```

### Community Saint Thomas Hospital

```{r}
id4233_doc_data <-read_csv('../data/id4233_doc_count.csv') 
```

```{r}
id4233_doc_df <- full_join(sample_shapefile,
                    id4233_doc_data%>%
                      mutate(zip=as.character(zip))
                    ) %>% 
          replace(is.na(.), 0) #replace all NAs in df with zeros for choropleth mapping
```

```{r}
id4233_doc_df %>%
  ggplot(aes(fill=patient_count)) +
  geom_sf(color=NA) + #set 
  #coord_sf(crs=)
  scale_fill_gradientn(colours = c("grey80", "cyan", "magenta"), values = c(0,0.001,1)) +
  coord_sf(datum = NA) +
  labs(fill= 'Number of referrals',
      title = 'Saint Thomas Hospital') +
  theme_minimal()
```


### Three communities together

```{r}
com_3_data <-read_csv('../data/community_3.csv') 
```

### Cross Join

```{r}
### Use crossing function to avoid having '0' where communities have no zipcode value to avoid having a map with values 0 only for the facet_wrap
cross_join <- crossing(communityId = c(4228, 4233, 4238), zip = sample_shapefile %>% pull(zip))
```


```{r}
### Full Join
com3_merge_data <- full_join(cross_join,
                    com_3_data%>%
                      mutate(zip=as.character(zip))
                    )%>% 
          replace(is.na(.), 0) #replace all NAs in df with zeros for choropleth mapping
```
```{r}
com3_merge_df <- full_join(sample_shapefile,
                    com3_merge_data %>%
                      mutate(zip=as.character(zip))
                    )%>% 
          replace(is.na(.), 0) #replace all NAs in df with zeros for choropleth mapping
```


```{r}
com3_merge_df$communityId[com3_merge_df$communityId  == 4228]  <-  "HCA Hospitals"
com3_merge_df$communityId[com3_merge_df$communityId  == 4238]  <-  "Vanderbilt University Medical Center"
com3_merge_df$communityId[com3_merge_df$communityId  == 4233]  <-  "Saint Thomas Hospitals"
```


```{r Test}

com3_merge_df %>%
  ggplot(aes(fill=count)) +
  geom_sf(color='grey50') + #set 
  #coord_sf(crs=)
  scale_fill_gradientn(colours = c("white", "cyan", "magenta"), values = c(0,0.001,1)) + 
  coord_sf(datum = NA) +
  labs(fill= 'Number of \nreferrals',
      title = 'Number of Referrals for three main communities by zipcodes') +
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~communityId)
```
### Use a log function since the communities numbers are different

```{r different settings}

facet_1 <- com3_merge_df %>%
  ggplot(aes(fill=count)) +
  geom_sf(color=NA) + 
  scale_fill_gradientn(colours = c("grey80", "cyan", "magenta"), 
                       values = c(0,0.001,1),
                       breaks = c(10, 25, 100, 400),
                       labels = c(10, 25, 100, 400),
                       trans = 'log1p') + #log
  coord_sf(datum = NA) +
  labs(fill= 'Number of \nreferrals',
      title = '                  Number of Referrals for three main communities by zipcodes') +
  facet_wrap(~communityId)

facet_1
```


```{r Final with a log}

facet_2 <- com3_merge_df %>%
  ggplot(aes(fill=count)) +
  geom_sf(color="grey50") + 
  scale_fill_gradientn(colours = c("white", "cyan", "magenta"), 
                       values = c(0,0.001,1),
                       breaks = c(10, 25, 100, 400),
                       labels = c(10, 25, 100, 400),
                       trans = 'log1p') + #log
  coord_sf(datum = NA) +
  labs(fill= 'Number of \nreferrals') +
  ggtitle("Number of Referrals by ZIP code to Three Main Communities") +
  theme(plot.title = element_text(hjust = 0.5)) +
  facet_wrap(~communityId)
#fig <- ggplotly(facet_2) 
facet_2
```

```{r}
ggsave("facet_2.png", width = 8, height = 4, dpi = 700)
```

#Publish to plotly
```{r}
api_create(facet_2, filename = "community_louvain_map")
```